\documentclass[12pt, reqno]{amsart}
\pdfoutput=1
\usepackage{mathpreamble}

\title{Response to comments on galley proofs}
\author{Sayantan Khan}
\address{Department of Mathematics, University of Michigan, Ann Arbor, MI}
\email{\href{mailto:saykhan@umich.edu}{saykhan@umich.edu}}
\urladdr{\url{https://www-personal.umich.edu/~saykhan/}}


\date{\today}

\begin{document}

\maketitle

\section{Keywords, MSC classification, and postal address}
\label{sec:keyw-msc-class}

The keywords look good, however I'd like to add an additional phrase: ``geometrically finite groups'', so the new keywords are ``Mapping class group, Teichmüller space, Thurston boundary, geometrically finite groups''.

An appropriate secondary MSC2020 label would be 37E35 (Flows on surfaces).

The postal address listed in the paper is indeed both complete and accurate.

\section{Response to questions}
\label{sec:sugg-chang}

Here is some clarification for the confusing sentences, and other questions.
\begin{itemize}
\item (5) ``Have'' should be replaced with ``has'', since it's a singular set we're talking about. With regards to the lower Hausdorff dimension, the full sentence should read as follows: ``the set of minimal IETs with flips has a lower Hausdorff dimension than the set of all IETs with flips''. I hope that addition clarifies the sentence.
\item (8) I agree that the rearrangement makes sense, and avoids sounding repetitive.
\item (12) I've seen both orientation double cover, and orientable double cover being used in the literature, but it appears that the former is more common; I agree with changing orientation double cover to orientable double cover.
\item (17) I'm not sure what dynamic parens mean? Does it mean they adjust their size based on the contents inside? In any case, it looks alright to me.
\item (18) The sentence is actually missing several words. The corrected sentence reads as follows: ``For the quadratic differential $q$ in Figure 1, the complex lengths of $a$ and $a^{\prime}$ must be conjugates of each other, the complex lengths of $b$ and $b^{\prime}$ must be negative conjugates of each other, and the complex lengths of $c$ and $c^{\prime}$ must be real.''
\item (43) I agree there needs to be punctuation at the end of the sentence. I prefer a period rather than a colon though.
\end{itemize}

\section{Changes seeking approval}
\label{sec:chang-seek-appr}

Here is a list of suggested changes/changes seeking approval that I agree with.

\begin{itemize}
\item (1)
\item (2)
\item (3)
\item (4)
\item (6)
\item (7)
\item (9)
\item (10)
\item (11)
\item (13)
\item (14)
\item (15)
\item (16)
\item (19)
\item (20)
\item (21)
\item (22)
\item (23)
\item (24)
\item (25)
\item (26)
\item (27)
\item (28)
\item (29)
\item (30)
\item (31)
\item (32)
\item (33)
\item (34)
\item (35)
\item (36)
\item (37)
\item (38)
\item (39)
\item (40)
\item (41)
\item (42)
\end{itemize}


\end{document}